---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# gganonymize

[![Travis build status](https://travis-ci.org/EmilHvitfeldt/gganonymize.svg?branch=master)](https://travis-ci.org/EmilHvitfeldt/gganonymize)

The goal of gganonymize is to anonymize the labels and text in a ggplot2 object in such a way that vizualizations about sensitive information can more easily be shared and critiqued. 

## Installation

You can install the development version from Github using `devtools`:

``` r
# install.packages("devtools")
devtools::install_github("EmilHvitfeldt/gganonymize")
```

## Examples

`gganonymize` will replace the text in the title, subtitle, caption and tag with similar length text while ignoring numerics.

```{r}
library(ggplot2)
library(gganonymize)

ggg <- ggplot(mtcars, aes(as.factor(cyl))) +
  geom_bar() +
  labs(title = "Test title",
       subtitle = "Test subtitle, this one have a lot lot lot lot lot more text then the rest",
       caption = "Test caption",
       tag = 1) +
  facet_wrap(~vs)

gganonomize(ggg)
```

It will respect names of of columns used in multiple settings such that the legend will match.

```{r}
ggg <- ggplot(mtcars, aes(mpg, disp, color = disp, shape = factor(am))) +
  geom_point()

gganonomize(ggg)
```

Likewise will it sepect names in character/factor variables.


```{r}
ggg <- ggplot(mpg, aes(class, fill = class)) +
  geom_bar()

gganonomize(ggg)
```

and in facet labels.

```{r}
ggg <- ggplot(mpg, aes(cty, displ, color = class)) +
  geom_point() +
  facet_wrap(~ class)

gganonomize(ggg)
```

This also extends to geom_label, 

```{r}
ggg <- ggplot(iris, aes(Sepal.Length, Sepal.Width, label = Species)) +
  geom_label()

gganonomize(ggg)
```

and geom_text.

```{r}
ggg <- ggplot(iris, aes(Sepal.Length, Sepal.Width, label = Species)) +
  geom_text()

gganonomize(ggg)
```

